Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Reverted back to having all ethnicity data in one tibble, rather than separated by white/non-white

```{r Recode ethnicity levels and filter data}

@@

#Filter White participants per sample

dat.retro_ethnicity_white <- dat.retro_ethnicity_plot %>% 
  group_by(Sample_plot, Ethnicity_collapsed) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  filter(Ethnicity_collapsed == "White")

#Filter non-white participants per study

dat.retro_ethnicity_non_white <- dat.retro_ethnicity_plot %>% 
  group_by(Sample_plot, Ethnicity_collapsed) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  filter(Ethnicity_collapsed != "White")

```{r Plot GLAD/EDGI NBR and RAMP ethnicity retro}

dat.retro_ethnicity_plot %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   labels = ethnicity_levels) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n), 
            position = position_dodge(width=0.9), 
            vjust=-0.25)

>>>>

```{r GLAD/EDGI NBR and RAMP ethnicity}

@@

dat.retro_ethnicity_plot <- dat.retro %>% 
  group_by(Sample_plot, Ethnicity_collapsed) %>% 
  summarise(n = n()) %>% 
  drop_na()

dat.retro_ethnicity_plot %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n), 
            position = position_dodge(width=0.9), 
            vjust=-0.25)
